% \newcommand*\numi{nvm\=i}

\section{Frequently Asked Questions}
\begin{description}
    \item[Wow the bibliography is super long, did Mr. Whiskers read all that?] Sadly not yet. We have read a great deal of material, and are continuing to read more, so our reading list was printed in its entirety to give an air of how well read we are.
    
    \item[What is Proof of Meow\textsuperscript{\textregistered}?] It is a silly product name to go with Mr. Whiskers. The only protocol there is right now are text messages with "meow", "hiss", "purr", over simple telnet between two machines. 
    
    \item[Is it \compu or Proof of Meow\textsuperscript{\textregistered} really trademarked?] No. It just looks cool and completely silly to use them with the names. But the R with the circle is part of the Proof name.
    
    \item[What is \compu{}] The idea is to name the entity that includes the TM, if that is allowed. Like the circle "R" the name includes the superscript "TM" as part  of the name. 
    
    \item[What is \compu{}'s product?] We don't have anything at this moment. We have an idea, a prototype, and a vision of building a software toolkit called, World Domination Toolkit\textsuperscript{\textregistered} which does something. The tokens will be used in this system, maybe. 
    
    \item[Who is Mr. [Redacted] Whiskers?] Mr. Whisker's is our mascot and leader. He is also super cute. If it's really important we could probably pay someone to change their name to "Mr. Whiskers".  
    
    \item[What is Mr. Whiskers' first name?] It's "[Redacted]". duh.
    
    \item[Who is behind all of this?] A single developer is currently behind all of this. Currently I, ahem, Mr. Whiskers, is researching and developing a suite of tools and systems in the blockchain space but he is not ready to publish it. Mr. Whiskers is working towards on a number of related project which employ various tokens, secure tokens, permission-ed-block-chains and are applicable.  Mr. Whiskers will be making this work available as they mature. For now, this is an experiment to see how ERC-20 work.  Mostly to do something during the Chinese Holiday. 

    \item[What will you do with the money?] Any funds contributed to this token will be used to form the entity in Hong Kong or where ever and develop tools for Mr. Whiskers and the World Domination Toolkit for which the token will be used to do something, I don't know right now.
    
    \item[How do I know this is not a scam?] You don't. It's not, I am not making any promises for what the tokens are for and what you will get in return. If you have any concerns, please don't acquire any of these tokens. 
    
\end{description}
